%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Joshua}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Jackson}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Software Engineer II} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.35\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Huntsville, Alabama}\\
	\icon{Phone}{12}{+1 256 929 9093}\\
	\icon{At}{12}{\href{mailto:joshua.w.jackson@protonmail.com}{joshua.w.jackson@protonmail.com}}\\	
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\noindent
	I am a passionate technology geek seeking to push my skills and abilities to new levels. My 
	career has exposed me to a broad range of technologies, and it has been a humbling journey.
	I love learning about practically any topic, and I thrive in environments where learning is a constant requirement. I'm currently focused
	on sharpening my low-level programming abilities and reducing the number of abstractions between myself and the bare metal.\\ 
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{C\#}{100}
		\baritem{Javascript}{60}
		\baritem{Linux}{50}
		\baritem{Git}{70}
		\baritem{C}{40}
		\baritem{Python}{40}
	\end{barchart}
\end{minipage}

\begin{center}
	\bubbles{4/SQL, 2/NoSQL, 2/AWS, 5/Windows, 4/OOP, 2/Functional}
\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{2012 -- present}
		{Software Engineer II}
		{Cepeda Systems and Software Analysis}
		{Full-Stack Desktop application development providing aviation GIS mission planning capabilities for the Department of Defense.\\
		\begin{itemize}
			\item Created a WPF application for running tests in the production environment that generated a test report and traceability matrix, which reduced testing time from two weeks to one day.
			\item Fielded a REST web service for gathering user feedback during a test event on an isolated network, which reduced distractions and increased the quality of the feedback gathered during the event.
			\item Migrated the project from a custom dependency management solution to Nuget, which provided increased stability for upstream teams while eliminating the bus factor associated with the custom approach.
		\end{itemize}
		\texttt{C\#}\slashsep\texttt{Visual Studio}\slashsep\texttt{Windows}\slashsep\texttt{Azure Dev Ops}}
	\entry
		{Sept. 2018 -- 2020\\\footnotesize{part time}}
		{Lead Developer}
		{Cepeda Systems and Software Analysis}
		{Serverless web application for facilitating CMMI appraisals.\\
		\begin{itemize}
			\item Architected the application using AWS for the back-end (Lambda, Cognito, S3, DynamoDB, API Gateway) and React+Bootstrap for the front-end.
			\item Created scripts using the Serverless Framework and NPM for deploying the back-end and front-end automatically. 
			\item Integrated the project with Electron, which provided equivalent functionality as a Desktop application while reusing existing code.
		\end{itemize}
		\texttt{JS}\slashsep\texttt{React}\slashsep\texttt{AWS}\slashsep\texttt{Node.js}\slashsep\texttt{Electron}\slashsep\texttt{Git}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2007 -- 2012}
		{Bachelor's Degree}
		{University Of Alabama in Huntsville}
		{Computer Engineering - GPA 3.4}
\end{entrylist}

\cvsect{References}

\begin{entrylist}
	\entry{251 616 0420}{Ashley Sanders}{Former colleague and collaborator}{}
	\entry{256 461 1210}{Chase Marsh}{Architect and Lead Developer - AMPS}{}
	\entry{256 603 3519}{Tom Holt}{Former Architect and Lead Developer - AMPS}{}
\end{entrylist}

\end{document}
